### 2020-11-12 doc/manuscript/Dow_manuscript.Rmd
update title

**Title:** ~~Effect of spring temperatures on tree growth phenology in two temperate deciduous forests~~
Warmer spring temperatures in temperate deciduous forests cause earlier tree growth but have little/only modest(?) effect on annual woody productivity

@@

Cameron Dow^1^
Loïc D’Orangeville
Erika B. Gonzalez-Akre^1^,
Ryan Helcoski^1^,
Valentine Herrmann^1^,
Ian McGregor^1^,
Sean McMahon,
Albert Kim^1^,
David A. Orwig
Kristina J. Anderson-Teixeira^1,n^*

>>>>

**Title:** ~~Effect of spring temperatures on tree growth phenology in two temperate deciduous forests~~
Warmer spring temperatures in temperate deciduous forests cause earlier tree growth but have little effect on annual woody productivity

@@

Cameron Dow^1^,
Loïc D’Orangeville,
Erika B. Gonzalez-Akre^1^,
Ryan Helcoski^1^,
Valentine Herrmann^1^,
Ian McGregor^1^,
Sean McMahon,
Albert Kim^1^,
David A. Orwig,
Kristina J. Anderson-Teixeira^1,n^*
